Union and intersection contracts are hard, actually

### 2021-07-29 paper.tex
More citation fixes

The consequence is that \citeauthor{RootCauseOfBlame}~\cite{RootCauseOfBlame}
don't prove their system complete for the coinductive semantics.  It's probably
just an oversight in the proof: we believe their system to be indeed complete
for the coinductive semantics. But it does speak to the intrinsic complexity of
union and intersection contracts: it is remarkably easy to get details wrong.
This difficulty contrasts with the standard framework of higher-order contracts
where satisfaction is much more straightforward.

@@

Enforcing pre- and post-conditions at runtime is a widely established practice.
In their foundational paper~\cite{FindlerFelleisenHOContracts}, Findler and
Felleisen introduce higher-order contracts, a principled approach to run-time
assertion checking that nicely supports functions. They introduce the notion of
blame, which is crucial to good error reporting. It became apparent later that
their contracts are closely related to the type casts introduced by gradual
typing, excluding blame: both \cite{FindlerMultiLang} and
\cite{FelleisenInterLang} see the value of contracts as a safe interface between
typed and untyped code. In \cite{WellTypedBlamed}, the authors precisely
introduce a system integrating gradual typing with contracts \textit{à la
Findler \& Felleisen}. Nickel adopts a similar type system, with both statically
typed terms, dynamically typed terms, and first-class contracts. Higher-order
contracts are the basis of the work of \cite{KeilThiemannUnionIntersection}
and \cite{RootCauseOfBlame} that this paper explored extensively.

>>>>

The consequence is that \citeauthor{RootCauseOfBlame} don't prove their system
complete for the coinductive semantics.  It's probably just an oversight in the
proof: we believe their system to be indeed complete for the coinductive
semantics. But it does speak to the intrinsic complexity of union and
intersection contracts: it is remarkably easy to get details wrong.  This
difficulty contrasts with the standard framework of higher-order contracts where
satisfaction is much more straightforward.

@@

Enforcing pre- and post-conditions at runtime is a widely established practice.
In their foundational paper~\cite{FindlerFelleisenHOContracts}, Findler and
Felleisen introduce higher-order contracts, a principled approach to run-time
assertion checking that nicely supports functions. They introduce the notion of
blame, which is crucial to good error reporting. It became apparent later that
their contracts are closely related to the type casts introduced by gradual
typing, excluding blame: both \cite{FindlerMultiLang} and
\cite{FelleisenInterLang} see the value of contracts as a safe interface between
typed and untyped code. In \cite{WellTypedBlamed}, the authors precisely
introduce a system integrating gradual typing with contracts \textit{à la
Findler \& Felleisen}. Nickel adopts a similar type system, with both statically
typed terms, dynamically typed terms, and first-class contracts. Higher-order
contracts are the basis of the work of
\citeauthor{KeilThiemannUnionIntersection}~\cite{KeilThiemannUnionIntersection}
and \citeauthor{RootCauseOfBlame}~\cite{RootCauseOfBlame} that this paper
explored extensively.
